An Introduction to Return Oriented Programming

### 2023-02-16 paper.tex
changes

@@

  \item Determine how many bytes are needed to override the base pointer \Verb+ebp+

@@

\section{Results}
\paragraph{Attack}
After injecting the generated payload from \cref{sec:attack} as a command line argument the program opened a shell from which we can use privilege escalation techniques in order to completely compromise the system. The only compiler options that had to be activated were PIE and stack canaries. It is likely that there are systems still in use today which are vulnerable to this kind of attack. Since it allows almost arbitrary code execution it is very important to identify these devices and patch or replace them.
\paragraph{ASLR}
The information about wether or not ROP can be applied to systems with ASLR enabled is inconsistent. In the run with PIE and stack canaries disabled the attack still worked even with \Verb+/proc/sys/kernel/randomize_va_space+ set to \Verb+2+, meaning full randomization of the different segments like header, libraries and stack. This is probably due to PIE

\section{Protection}
Luckily we had to disable several security mechanisms to make this attack possible, especially

>>>>

\begin{figure}[h!]

@@

  \item Determine how many words are needed to override the base pointer \Verb+ebp+

@@

\subsection{Payload}
From all the previous steps the payload got constructed using python~\cref{code:payloadbinsh}.
\bltCode{payload.py}{python}{Payload to open /bin/sh}{code:payloadbinsh}
\section{Results}
\paragraph{Attack}
After injecting the generated payload from \cref{sec:attack} as a command line argument the program opened a shell from which we can use privilege escalation techniques in order to completely compromise the system. The only compiler options that had to be activated were PIE and stack canaries. It is likely that there are systems still in use today which are vulnerable to this kind of attack. Since it allows almost arbitrary code execution it is very important to identify these devices and patch or replace them.
\paragraph{ASLR}
The information about wether or not ROP can be applied to systems with ASLR enabled is inconsistent. In the run with PIE and stack canaries disabled the attack still worked even with \Verb+/proc/sys/kernel/randomize_va_space+ set to \Verb+2+, meaning full randomization of the different segments like header, libraries and stack. This is probably due to PIE

\section{Protection}
\paragraph{Stack canaries}
Stack canaries are one of the most effective approaches against ROP, they are enabled by default and prevent most forms of buffer overflows, however, stack canaries can be based on a small entropy pool and can therfore be bruteforced with an effort significantly smaller than regular bruteforcing. Depending on the target it can still be profitable and possible to bruteforce it even with a big entropy pool and high randomness.
\paragraph{NX}
The activation of the NX bit has no effect on ROP since the program never executes code outside the segments marked with the \bltInlineVerb{CODE} flag like in a classical stack overflow attack.
\paragraph{ASLR}
\paragraph{PIE}
